Comparison of Dimensionality Reduction Schemes for Parallel Global Optimization Algorithms

### 2018-09-24 2018/RSD/MultiEvolvents/slides/slides.tex
RSD: update slides

\title{Comparison of Dimensionality Reduction Schemes for Parallel Global Optimization Algorithms}
\author{\textbf{Konstantin~Barkalov}, \textbf{Vladislav~Sovrasov} and \textbf{Ilya~Lebedev}}
\institute{Lobachevsky State University of Nizhni Novgorod}
\date{}

@@

\begin{frame}
  \frametitle{Shifted and rotated evolvents}
  To create a fixed amount of preimages one can use a pre-defined set of different evolvents. These evolvents could be shifted or rotated versions of the original one. Set of shifted evolvents\footnote{Strongin, R.G., Gergel, V.P., Barkalov, K.A. Parallel methods for global optimization problem
solving (in Russian), 2009} is theoretically proven to generate at least one pair of close preimages if images are close and it perform better than the set of rotated curves.
  \begin{figure}[ht]
    \subfloat{\raisebox{.0\textheight}{\includegraphics[width=.35\textwidth]{shifted.pdf} }}
    \subfloat{{\includegraphics[width=.35\textwidth]{rotated.pdf} }}
  \end{figure}
\end{frame}

@@

>>>>

\title{Comparison of Dimensionality Reduction Schemes for Parallel Global Optimization Algorithms}
\author{\textbf{Konstantin~Barkalov}, \underline{\textbf{Vladislav~Sovrasov}} and \textbf{Ilya~Lebedev}}
\institute{Lobachevsky State University of Nizhni Novgorod}
\date{}

@@

\begin{frame}
  \frametitle{Shifted and rotated evolvents}
  To create a fixed amount of preimages one can use a pre-defined set of different evolvents. These evolvents could be shifted or rotated versions of the original one. Set of shifted evolvents\footnote{Strongin, R.G. Algorithms for multi-extremal mathematical programming problems employing the set of joint space-filling curves, Journal of Global Optimization 2(4), 357--378, 1992} is theoretically proven to generate at least one pair of close preimages if their images are close and it performs better than the a set of rotated curves in that sense.
  \begin{figure}[ht]
    \subfloat{\raisebox{.0\textheight}{\includegraphics[width=.35\textwidth]{shifted.pdf} }}
    \subfloat{{\includegraphics[width=.35\textwidth]{rotated.pdf} }}
  \end{figure}
\end{frame}

@@

\begin{frame}
  \frametitle{Cluster environment}
  \begin{center}

  The computational experiments have been carried out on the Lobachevsky supercomputer at  State University of Nizhni Novgorod.
  One node includes 2 Intel Sandy Bridge E5-2660 2.2 GHz processors and 64 GB RAM.

  Each node runs under CentOS 7 Linux with GCC 4.8 compiler and Intel MPI library.
\end{center}
